---
  title: "Assignment V: GitHub and the ticketmaster.com API"
subtitle: "Data Science Project Management | Winter Term 2020/21"
author: "Submitted by Franziska Müller (Student ID: 5401673)"
date: "February, 16, 2021"
output: 
  html_document:
  toc: true
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
I hereby assure that my submission is in line with the *Code of Conduct* outlined on the lecture slides. I worked on my own.

## General setup

Before I start the project, I clear my workspace and install (if necessary) and load the packages that are needed for the exercises (XXX). 
# Note regarding key and maybe working directory

```{r preparation, message = FALSE, warning = FALSE}
# Clear workspace
rm(list = ls())

# Check if packages have been installed before; if not, install them
if (!require("knitr")) install.packages("knitr")

# Load packages
library(knitr)

# Maybe note regarding individual working directory 

# Source private key
```

## Exercise 2: Getting to know the API

Rate limit is given by 5 requests per second and max. 5,000 requests per day. 