---
  title: "Assignment V: GitHub and the ticketmaster.com API"
subtitle: "Data Science Project Management | Winter Term 2020/21"
author: "Submitted by Franziska Müller (Student ID: 5401673)"
date: "February, 16, 2021"
output: 
  html_document:
  toc: true
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
I hereby assure that my submission is in line with the *Code of Conduct* outlined on the lecture slides. I worked on my own.

## General setup

Before I start the project, I clear my workspace. 
# Note regarding key and maybe working directory

```{r preparation, message = FALSE, warning = FALSE}
# Clear workspace
rm(list = ls())

# Maybe note regarding individual working directory 

# Source private key
```

## Exercise 2: Getting to know the API

Rate limit is given by 5 requests per second and max. 5,000 requests per day.


## Exercise 3: Interacting with the API - the basics

*Load the packages needed to interact with APIs using R.*
```{r packages, message = FALSE, warning = FALSE}
# Check if packages have been installed before; if not, install them
if (!require("jsonlite")) install.packages("jsonlite")
if (!require("httr")) install.packages("httr")
if (!require("rlist")) install.packages("rlist")
if (!require("tidyverse")) install.packages("tidyverse")
# if (!require("naniar")) install.packages("naniar")

# Load packages
library(jsonlite)  
library(httr)
library(rlist)
library(tidyverse)
# library(naniar)
```
